Molecular dynamics simulation of synchronization in driven particles

### 2021-02-26 manuscript/manuscript_ajp_2020.tex
updated text and rearranged to put parameters as the first exercise

  To study synchronization patterns, 
  it is useful to compare
  mode-locked quantities %periodic signals
  in a two dimensional phase plot. 
  In a non-driven system, an appropriate
  phase space is particle velocity $v_y$ versus position $y$.  
  For a particle driven parallel to the $y-$direction,
  %the particle velocity and position increase
  %in time. % due to $F^{dc}$.
  %Since a system does not form
  %a closed loop in
  %$v_y$ vs $y$ space,
  we define phase variables 
  to account for the net increase in velocity
  and position.
  The phase position is
  defined as 
  %within the substrate period as 
  %We define a phase variable 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \phi(t) = 2\pi (y(t)-\langle v_y \rangle t)/\lambda
  \end{equation}
  centered about the average particle displacement $\langle v_y \rangle t$
  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
  For clarity our plots are normalized by the prefactor $2\pi$. 
  %to compare $\phi(t)$ to $\lambda$.
  %In phase diagrams we plot $\phi(t)$ %phase
  %versus
  The phase velocity is
  \begin{equation}
    %(y mod \lambda) / \lambda
    \dot{\phi}(t) =2\pi (v_y(t)-\langle v_y \rangle) /\lambda.  % 
  \end{equation}
  With no landscape force, 
  the phase velocity will be zero when $F^d(t) = F^{dc}$.
  %Juniper %REF 53
  %and easily generated with a computer code 
  %or oscilloscope \cite{Tong1997}.
  When velocity
  is mode-locked to %repeat periodically
  a spatial location
  a closed loop appears in  
  phase space. % showing the relationship
  %between two periodic functions
  The pattern is determined by the mode,
  or frequency ratio,
  so a 1:1 mode appears as a circle or oval. 
  Nodes appear %in the oval 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is nearly phase locked
  will appear as an unclosed loop.
  Such quasiperiodic systems are
  not fully synchronized
  so the position-velocity relationship
  shifts in time.
  In Fig.~\ref{fig:phase}, 
  all cases exhibit some line thickening, 
  indicating the particle location and velocity
  are not fully synchronized,
  although this can be tuned by
  calculating $\langle v_y \rangle$ over
  shorter time ranges.
  %and the shifts in phase space represent
  %small changes in system behavior.
  %With a long simulation time,
  %a quasiperiodic phase diagram
  %fills the plotting region due to the gradual shift
  %in the velocity-position relationship.
  %with a frequency generator,
  %where two combined frequencies at perpendicular orientations
  %\footnote{The term phase
  %has two scientific meanings:  
  %oscillation phase $\phi_0$ is the constant of the argument
  %in a periodic function
  %$\sin{(\omega t + \phi_0)}$ and phase space is
  %used to characterize oscillating systems with
  %parametric plots.}.

  %OKAY, WHY AREN'T MY AMPLITIDES \phi \pm 2\pi and \dot{\phi} \pm 4\pi.
  In Fig.~\ref{fig:phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing %substrate amplitude $A_p$.
  $F^{dc}$, % and frequency $f = 0.01$ and $F^{ac} = 0.2$.
  with the remaining parameters fixed as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:phase}(a) with
  $F^{dc} = 0.04$
  the phase plot is a small closed oval
  centered at
  $(\phi,\dot{\phi})=(0.1,0)$.
  A small tail appears
  due to the initial transient
  motion of the particle.
  %with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
  %and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
  The particle is confined in a single
  substrate minima,
  and has no net velocity.
  In Fig.~\ref{fig:phase}(b)
  with $F^{dc} = 0.07$
  the phase loop is a symmetric trianglar shape,
  indicating a 1:1 match between
  particle motion and velocity consistent with 
  Fig.~\ref{fig:0}(a).
  The maximum $\dot{\phi}$ %with a 1:1 mode locking,
  occurs at $\phi \sim 0.4$,
  and maximum $\phi$ occurs
  when $\dot{\phi} \sim 0$.

  %The dynamical properties are asymmetric,
  %with three nodes in the positive $\dot{\phi}$ values.
  %[insert analysis.]
  As $F^{dc}$ %the constant driving force 
  increases,
  nodes form in the phase diagram
  that occur due to repeated values
  of $\dot{\phi}$ over multiple phase positions.
  The motion becomes quasiperiodic
  so the loops in phase space do not fully overlap.
  In Fig.~\ref{fig:phase}(c)
  with $F^{dc} = 0.1$
  two nodes form.
  The particle moves across $2\lambda$
  during one time period.
  In Fig.~\ref{fig:phase}(d)
  with $F^{dc} = 0.125$
  three nodes form as the particle moves across $3\lambda$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{phase.pdf}
      %\vspace*{-3cm}
      \caption{
        Phase plot of a particle with $F^{dc} = $ (a) $0.04$, (b) $0.07$, (c) $0.1$, (d) $0.125$.  These values are marked as black circles
        in Fig.~\ref{fig:1}.%, (e) $0.25$ and (f) $0.3$.
      The other parameters
      are $F^{ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
      as Fig.~\ref{fig:0}.}
      \label{fig:phase}
    \end{figure}

In Section ~\ref{sec:problems}
we explore our model
with suggested exercises for interested readers.
We include analytic exercises to examine the 
to linear drag equation in Ex.~\ref{ex:reynolds}, 
the equation of motion in Ex.~\ref{ex:n2l},
and 
numerical integration techniques in Ex.~\ref{ex:euler}.
We extend the model with
numerical exercises %extend the model
to include finite temperature effects
in Ex.~\ref{ex:brownian}.
We explore changes in the particle motion
with parameter changes in Ex.~\ref{ex:parameters}.
%Methods to visualize the dynamics of the particle motion
%are in Ex.~\ref{ex:animation}.
%In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.

\section{Associated problems}
\label{sec:problems}	% You can label sections for reference
%\begin{enumerate}
%\item
\subsection{Drag Models and Reynolds Numbers.}
Stokes' law describes the drag force
$\vec{F}^{lin} = -3 \pi \eta D \vec{v}$ 
on a sphere
moving through a viscous liquid at velocity $\vec{v}$ 
  where $\eta$ is the dynamic fluid viscosity and 
  $D$ is the particle diameter \cite{Taylor2005}.
  In simulation we
  subsume the constants $3 \pi D$
  such that $3 \pi D \eta \rightarrow \eta $.
  %
  Often drag forces are
  modeled as a polynomial series ~\cite{Taylor2005}
  \begin{equation}
    \vec{F}^{drag} = -b \vec{v} - c v^2 \hat{v} + \ldots  .
  \end{equation}
  %This model should be familiar to readers
  %of a standard classical mechanics text, such as Ref.
  %when studying 
  %models Millikan's oil drops.
  Truncating the series to the first term
  is justified by demonstrating the sphere
  has a low Reynolds number  
  $R = D v \rho / \eta$
  where $\rho$ is the fluid density and $v$ the particle's speed.
  When $R$ is small, the quadratic and higher order terms
  may be ignored in favor of the linear drag term.

@@

  Fig.~\ref{fig:hops}
  shows the effects of lowering the frequency
  of applied driving force
  We hold the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies
  since $F^{dc} - F^{ac}= 0.05$
  is too small to overcome $A_p$.
  The rate of forward hops 
  increases as frequency decreases,
  but in each case the particle
  hops across two substrate periods as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
  do not match the temporal period of $F^d(t)$
  due to the high frequency.
  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.1$
  is apparent in the undulations of the particle
  with a period of $10\tau$.
  %Due to the high frequency,
  The particle is trapped between substrate minima $y \approx \lambda/2 $ for
  a time interval of $400 \tau$.
  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.05$
  with a period of $20\tau$
  arrests the particle between minima,
  with a hopping rate of $200 \tau$.
  At intermediate frequencies 
  such as $f=0.01$
  the particles are synchronized so that 
  the hopping rate matches the driving frequency.
  In Fig.~\ref{fig:hops}(c) $f=0.015$
  the particle hops forward two minima every $67\tau$.
  Low frequencies
  result in sustained positive motion of a particle.
  In Fig.~\ref{fig:hops}(d) $f=0.005$
  the particle executes two subsequent forward hops
  before becoming trapped
  for the remainder of the period $200 \tau$.
  In Fig.~\ref{fig:hops}(e) $f=0.001$
  the hopping is continuous
  over the simulation time.
  Here the particle reaches the top edge of the system
  and wraps back to $y=0$.
  Given a simulation time of the period length $1000 \tau$,
  the particle would cease forward motion.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.1$,
        (b) $0.05$, (c) $0.015$, (d) $0.005$ and (e) $0.001$ where  
        the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  %In Fig.~\ref{fig:hops}

  Hopping patterns with backward steps are more difficult
  to achieve than forward.
  In Ref.\cite{Juniper2015}
  experiments with single colloids 
  produce 
  the following
  combinations of forward and backwards steps:
  $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$
  %were realized 
  by sweeping through
  a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
  {\bf Find the parameters
  that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
  %[well, go on...]

  In Fig.~\ref{fig:hops_back}
  we explore a hopping pattern not
  observed in Ref.~\cite{Juniper2015}.
  This is possible in simulation because
  our particle readily hops through
  $2\lambda$.
  We fix $f=0.01$, $F^{dc}=0.1$, and $A_p = 0.1$
  and increase
  the amplitude of $F^{ac}$,
  which causes the number of backwards steps to increase.
  The number of forward steps also increases
  due to the increased total positive amplitude of $F^d(t)$.
  In Fig.~\ref{fig:hops_back}(a) 
  $F^{ac} = 0.2$. %, $0.3$ and $0.4$.
  %of the system for our original parameters.
  the number of backwards steps
  $n_b = 0$ with $n_f = 6$.
  In Fig.~\ref{fig:hops_back}(b) 
  $n_b = 2$ and $n_f = 8$.
  In Fig.~\ref{fig:hops_back}(c) 
  $n_b = 4$ and $n_f = 10$.
  In each case the average velocity %net displacement
  is $\langle v_y \rangle = 6\lambda/T$.

    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac}$.
        (a) The particle moves forward six minima with no steps backward.
        (b) The particle moves forward eight minima with two steps backward.
        (c) The particle moves forward nine minima with four steps backward.
      }
      \label{fig:hops_back}
    \end{figure}

  In Fig.~\ref{fig:shapiro}
  we sweep the constant driving force $F^{dc}$
  for a fixed amplitude $F^{ac}$ and frequency $f=0.1$.
  In the high frequency limit,
  the steps are separated
  by linearly increasing regions.

  Fig.~\ref{fig:shapiro}(a) shows $F^{ac}= 0.0$ and (b) shows $F^{ac}=0.4$
  with frequency $f=0.01$.

  The particle does not phase lock since there is no periodicity to $F^d(t)$,
  but does exhibit undulations in $\langle v_y \rangle$
  due to the corregations in the substrate.
  %WAIT, THAT DOESN'T MAKE SENSE!
  %WHAT IS WRONG WITH YOUR MD SIMULATION?
  When $F^{ac}=0.4$, 
  mode-locked steps appear in $\langle v_y \rangle$ vs. $F^{dc}$.
  At low values of $F^{dc}$ the particle may move backwards,
  distorting the steps, as seen below $F^{dc}<0.3$
  Between $0.3< F^{dc}<0.5$ the system exhibits phase locked steps.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig7}.pdf}
      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
      \caption{
        $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
        $F^{ac}=0.1$ (blue), $F^{ac}=0.2$ (orange),
        $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
        with frequency $f=0.0$.
        The substrate is as in Fig.~\ref{fig:0}
        with $A_p = 0.1$.
      }
      \label{fig:shapiro}
    \end{figure}
  %In Fig.~\ref{fig:hops}
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item
  %\subsection{Visualizing motion}
  %\label{ex:animation}
  %Drawing the contour 
  %The code for generating
  %a two dimensional colored plot
  %of the potential landscape
  %is calculated by evaluating
  %the analytic function in Eq.~\ref{eq:ysubstrate}
  %for a grid of values $(x_n,y_n)$.
  %is included in the supplementary material,
  %{\it I have python code that does all of this, but I don't have it
  %  set up to play nice with my new python MD code} 
  %Also the animation library in python...

>>>>

  To study synchronization patterns, 
  it is useful to compare
  mode-locked quantities %periodic signals
  in a two dimensional phase plot. 
  In a non-driven system, an appropriate
  phase space is particle velocity $v_y$ versus position $y$.  
  For a particle driven parallel to the $y-$direction,
  %the particle velocity and position increase
  %in time. % due to $F^{dc}$.
  %Since a system does not form
  %a closed loop in
  %$v_y$ vs $y$ space,
  we define phase variables 
  to account for the net increase in velocity
  and position.
  The phase position is
  defined as 
  %within the substrate period as 
  %We define a phase variable 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \phi(t) = 2\pi (y(t)-\langle v_y \rangle t)/\lambda
  \end{equation}
  centered about the average particle displacement $\langle v_y \rangle t$
  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
  For clarity our plots are normalized by the prefactor $2\pi$. 
  %to compare $\phi(t)$ to $\lambda$.
  %In phase diagrams we plot $\phi(t)$ %phase
  %versus
  The phase velocity is
  \begin{equation}
    %(y mod \lambda) / \lambda
    \dot{\phi}(t) =2\pi (v_y(t)-\langle v_y \rangle) /\lambda.  % 
  \end{equation}
  With no landscape force, 
  the phase velocity will be zero when $F^d(t) = F^{dc}$.
  %Juniper %REF 53
  %and easily generated with a computer code 
  %or oscilloscope \cite{Tong1997}.
  When velocity
  is mode-locked to %repeat periodically
  a spatial location
  a closed loop appears in  
  phase space. % showing the relationship
  %between two periodic functions
  The pattern is determined by the mode,
  or frequency ratio,
  so a 1:1 mode appears as a circle or oval. 
  Nodes appear %in the oval 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is nearly phase locked
  will appear as an unclosed loop.
  Such quasiperiodic systems are
  not fully synchronized
  so the position-velocity relationship
  shifts in time.
  In Fig.~\ref{fig:phase}, 
  all cases exhibit some phase shifts %line thickening, 
  indicating the particle location and velocity
  are not fully synchronized,
  although this can be tuned by
  calculating $\langle v_y \rangle$ over
  shorter time ranges.
  %and the shifts in phase space represent
  %small changes in system behavior.
  %With a long simulation time,
  %a quasiperiodic phase diagram
  %fills the plotting region due to the gradual shift
  %in the velocity-position relationship.
  %with a frequency generator,
  %where two combined frequencies at perpendicular orientations
  %\footnote{The term phase
  %has two scientific meanings:  
  %oscillation phase $\phi_0$ is the constant of the argument
  %in a periodic function
  %$\sin{(\omega t + \phi_0)}$ and phase space is
  %used to characterize oscillating systems with
  %parametric plots.}.

  %OKAY, WHY AREN'T MY AMPLITIDES \phi \pm 2\pi and \dot{\phi} \pm 4\pi.
  In Fig.~\ref{fig:phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing %substrate amplitude $A_p$.
  $F^{dc}$, % and frequency $f = 0.01$ and $F^{ac} = 0.2$.
  with the remaining parameters fixed as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:phase}(a) with
  $F^{dc} = 0.04$
  the phase plot is a small asymmetric curve.
  %centered at
  %$(\phi,\dot{\phi})=(0.1,0)$.
  A tail appears
  due to the initial transient
  motion of the particle.
  %with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
  %and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
  The particle is confined in a single
  substrate minima,
  and has no net velocity.
  The asymmetry is caused by bias induced by $F^{dc}$.
  In Fig.~\ref{fig:phase}(b)
  with $F^{dc} = 0.07$
  the phase loop is a symmetric trianglar shape,
  indicating a 1:1 match between
  particle motion and velocity consistent with 
  Fig.~\ref{fig:0}(a).
  %The maximum $\dot{\phi}$ %with a 1:1 mode locking,
  %occurs at $\phi \sim 0.4$,
  %and maximum $\phi$ occurs
  %when $\dot{\phi} \sim 0$.
  %
  %The dynamical properties are asymmetric,
  %with three nodes in the positive $\dot{\phi}$ values.
  %[insert analysis.]
  As $F^{dc}$ %the constant driving force 
  increases,
  nodes form in the phase diagram
  that occur due to repeated values
  of $\dot{\phi}$ over multiple phase positions.
  %The motion becomes quasiperiodic
  %so the loops in phase space do not fully overlap.
  In Fig.~\ref{fig:phase}(c)
  with $F^{dc} = 0.1$
  two nodes form.
  The particle moves across $2\lambda$
  during one time period.
  In Fig.~\ref{fig:phase}(d)
  with $F^{dc} = 0.125$
  three nodes form as the particle moves across $3\lambda$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{phase.pdf}
      %\vspace*{-3cm}
      \caption{
        Phase plot of $\dot{\phi(t)}/(2\pi)$ vs. $\phi(t)/(2\pi)$.
        The particle is driven with $F^{dc} = $ (a) $0.04$, (b) $0.07$, (c) $0.1$, (d) $0.125$.  These values are marked as black circles
        in Fig.~\ref{fig:1}. %, (e) $0.25$ and (f) $0.3$.
      The other parameters
      are $F^{ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
      as Fig.~\ref{fig:0}.}
      \label{fig:phase}
    \end{figure}

In Section ~\ref{sec:problems}
we explore our model
with suggested exercises for interested readers.
We explore changes in the particle motion
with parameter changes in Ex.~\ref{ex:parameters}.
We include analytic exercises to examine the 
to linear drag equation in Ex.~\ref{ex:reynolds}, 
the equation of motion in Ex.~\ref{ex:n2l},
and 
numerical integration techniques in Ex.~\ref{ex:euler}.
We extend the model with
numerical exercises %extend the model
to include finite temperature effects
in Ex.~\ref{ex:brownian}.
%Methods to visualize the dynamics of the particle motion
%are in Ex.~\ref{ex:animation}.
%In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.

\section{Associated problems}
\label{sec:problems}	% You can label sections for reference
%\begin{enumerate}
%\item

  Fig.~\ref{fig:hops}
  shows the effects of lowering the frequency
  of applied driving force
  We hold the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies
  since $F^{dc} - F^{ac}= 0.0$.
  %is too small to overcome $A_p$.
  The rate of forward hops 
  increases as frequency decreases,
  but in each case the particle
  hops across one substrate periods as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
  do not match the temporal period of $F^d(t)$
  due to the high frequency.
  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.05$
  is apparent in the undulations of the particle
  with a period of $20\tau$.
  %Due to the high frequency,
  The particle is trapped between substrate minima.
  %$y \approx \lambda/2 $ for
  %a time interval of $400 \tau$.
  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.022$
  with a period of $45\tau$
  arrests the particle between minima,
  with a hopping rate of seven periods ($320\tau$).
  At intermediate frequencies 
  such as $f=0.01$
  the particles are synchronized so that 
  the hopping rate matches the driving frequency,
  as in Fig.~\ref{fig:2}
  In Fig.~\ref{fig:hops}(c) $f=0.005$
  the particle hops forward two minima every period of $200\tau$.
  Low frequencies
  result in sustained positive motion of a particle.
  In Fig.~\ref{fig:hops}(e) $f=0.001$
  the hopping is continuous
  over the time $100 \tau < t < 400 \tau$,
  with the cycle repeating 
  over the period length $1000 \tau$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.07$ and $F^{ac} = 0.07$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.05$, 
        (b) $0.022$, (c) $0.005$ and (d) $0.001$. %where  
        %the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  %In Fig.~\ref{fig:hops}

  Hopping patterns with backward steps are more difficult
  to achieve than forward.
  In Ref.~\cite{Juniper2015}
  experiments with single colloids 
  produce 
  the following
  combinations of forward and backwards steps:
  $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$
  %were realized 
  by sweeping through
  a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
  %{\bf Find the parameters
  %that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
  %[well, go on...]

  In Fig.~\ref{fig:hops_back}
  we fix $f=0.01$, $F^{dc}=0.07$, and $A_p = 0.1$
  and increase
  the amplitude of $F^{ac}$.
  This causes the number of backwards steps to increase.
  The number of forward steps also increases
  due to the increased total positive amplitude of $F^d(t)$.
  In Fig.~\ref{fig:hops_back}(a) 
  $F^{ac} = 0.2$ %, $0.3$ and $0.4$.
  %of the system for our original parameters.
  the number of backwards steps
  $n_b = 0$ with $n_f = 4$.
  In Fig.~\ref{fig:hops_back}(b) $F^{ac} = 0.4$
  $n_b = 2$ and $n_f = 6$.
  %In Fig.~\ref{fig:hops_back}(c) 
  %$n_b = 4$ and $n_f = 10$.
  In each case the average velocity %net displacement
  is $\langle v_y \rangle = 4\lambda f$,
  which can be reproduced over a variety of $F^{ac}$ values.

    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac} = $
        (a) $0.2$ and
        (b) $0.4$.
      }
      \label{fig:hops_back}
    \end{figure}

    In Fig.~\ref{fig:shapiro}
    we sweep the constant driving force $F^{dc}$
    for a fixed amplitude $F^{ac}$ and frequency $f=0.01$.
    In the high frequency limit,
    the regions of phase locking
    are separated by regions of $F^{dc}$
    that do not phase lock,
    and appear to increase linearly with increasing $F^{dc}$.
    The width of the phase locked steps
    grows with increasing $F^{ac}$,
    since 
    the particle may move backwards
    over a broader range of $F^{dc}$.
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig7}.pdf}
      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
      \caption{
        $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
        $F^{ac}=0.1$ (blue), $F^{ac}=0.2$ (orange),
        $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
        with frequency $f=0.0$.
        The substrate is as in Fig.~\ref{fig:0}
        with $A_p = 0.1$.
      }
      \label{fig:shapiro}
    \end{figure}
  %In Fig.~\ref{fig:hops}
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item
  %\subsection{Visualizing motion}
  %\label{ex:animation}
  %Drawing the contour 
  %The code for generating
  %a two dimensional colored plot
  %of the potential landscape
  %is calculated by evaluating
  %the analytic function in Eq.~\ref{eq:ysubstrate}
  %for a grid of values $(x_n,y_n)$.
  %is included in the supplementary material,
  %{\it I have python code that does all of this, but I don't have it
  %  set up to play nice with my new python MD code} 
    %Also the animation library in python...

\subsection{Drag Models and Reynolds Numbers.}
Stokes' law describes the drag force
$\vec{F}^{lin} = -3 \pi \eta D \vec{v}$ 
on a sphere
moving through a viscous liquid at velocity $\vec{v}$ 
  where $\eta$ is the dynamic fluid viscosity and 
  $D$ is the particle diameter \cite{Taylor2005}.
  In simulation we
  subsume the constants $3 \pi D$
  such that $3 \pi D \eta \rightarrow \eta $.
  %
  Often drag forces are
  modeled as a polynomial series ~\cite{Taylor2005}
  \begin{equation}
    \vec{F}^{drag} = -b \vec{v} - c v^2 \hat{v} + \ldots  .
  \end{equation}
  %This model should be familiar to readers
  %of a standard classical mechanics text, such as Ref.
  %when studying 
  %models Millikan's oil drops.
  Truncating the series to the first term
  is justified by demonstrating the sphere
  has a low Reynolds number  
  $R = D v \rho / \eta$
  where $\rho$ is the fluid density and $v$ the particle's speed.
  When $R$ is small, the quadratic and higher order terms
  may be ignored in favor of the linear drag term.

@@
